### 2020-06-03 system-model.tex
:pencil: Fix typo
:sparkles: Separate waveform and split ratio

					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,n}^{(i-1)} \boldsymbol{C}_0\\

@@

					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\

@@

				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}

@@

			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method. $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\omega}, \omega \in [0,2\pi]$. The algorithm is summarized in Algorithm \ref{al:fs_waveform}.

>>>>

					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,0}^{(i-1)} \boldsymbol{C}_{I,0}\\

@@

					&\quad+\frac{3}{8} \beta_4 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\

@@

				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint_1}}

@@

			Note that objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} involve bilinear terms $\rho^{(i)}\mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})$ and $(1-\rho)W_{I,n,n}$, which can be lower bounded by partial Taylor expansion as in \ref{eq:bilinear_begin} -- \ref{eq:bilinear_end}.
					\rho^{(i)}\mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})
					& = \frac{1}{4}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2\label{eq:bilinear_begin}\\
					& \ge \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i-1)}\boldsymbol{W}_{I/P}^{(i-1)})\right)\nonumber\\
					& \quad \quad - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i-1)}\boldsymbol{W}_{I/P}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2\\
					\bar{\rho}^{(i)}W_{I,n,n}^{(i)}
					& = \frac{1}{4}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)^2 - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\\
					& \ge \frac{1}{2}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right) - \frac{1}{4}\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right)^2 - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\label{eq:bilinear_end}
					z'(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
					& = \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i-1)}\boldsymbol{W}_{I}^{(i-1)})\right) - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)^2\nonumber\\
					& \quad + \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right) - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)^2\label{eq:z'}\\
					g(\bar{\rho}^{(i)},W_{I,n,n}^{(i)})
					& = \frac{1}{2}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right) - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\label{eq:g}
			Therefore, problem \ref{op:su_waveform} is transformed to
				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform_final}}{}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g(\bar{\rho},W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
			where $\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)$ and $g(\bar{\rho},W_{I,n,n})$ are given in \ref{eq:z'} and \ref{eq:g}, respectively. We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method. $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\omega}, \omega \in [0,2\pi]$. The algorithm is summarized in Algorithm \ref{al:fs_waveform}.
